Quantum-assisted unsupervised data clustering

### 2020-05-06 manuscript.tex
resolving issue #26

In comparison with the circuits for Hamming distance calculations proposed previously \cite{trugenberger2001}, 
our method allows one to reduce the number of gates in the circuit (at least in $2n$ one-qubit NOT gates)
and reconstruct all distance matrix in parallel and can be implemented with high fidelity.

>>>>

Currently available quantum platforms are still subject to substantial level of noise and extracting the exact distance from amplitude is still a difficult task. However, for most of algorithms, SOFM included, the information of nearest vectors is sufficient. Because of that property, those algorithms fall into a special case category for which, as there is only one input vector considered, the ``Decoding'' stage (Fig.\ref{fig:qcircuit}) can be removed as measurement no longer needs to indicate for which input vector the distance has been measured. In this special case scenario the circuit depth complexity is matching with \cite{shuld2014}, but in general case for multiple input vectors the ``Decoding`` stage still needs to be included leading to larger circuit depth and less attractive complexity in terms of number of controlled gate operations. The number of controlled gate operations in this general case of multiple input vectors is matching the number of controlled gate operations in \cite{trugenberger2001}.
